Spin canonical divisors of log stacky curves

### 2015-06-21 stacky_write_up/spin_cring.tex
minor AD-ii wording edit
half of theorem in section 3

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}

@@

We will sketch a proof by induction.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$.  He finds generators in degrees up to $\beta$ and relations that are all quadratic in the generators (and thus lying in degrees at most $2\beta$).  We can ind

>>>>

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}
\newcommand \Supp{\text{Supp}}
\newcommand \initial{\text{in}}

@@

We will prove this by induction using methods analogous to ones of VZB\todo{add reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$:
\begin{lem}\label{lem:O'Dorney_1_point}
Let 
\[
	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
\] 
be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
\end{lem}
\begin{proof}
See O'Dorney \todo{provide reference}.
\end{proof}

The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.

\begin{lem}\label{lem:deg_1_saturation_induction}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.  Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that 
\begin{equation}\label{lem:deg_1_saturation_induction_dimension_condition}
h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:d\ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the nonnegative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
\[
	\initial_\prec(I')=\initial_\prec(I) k[u,x_1,...,x_m,y_1,...,y_n]+\langle y_ix_j: 1\le i\le n, 1\le j\le m\rangle+\langle y_iy_j: 1\le i\le j\le n-1\rangle.
\]
\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
\end{itemize}
\end{lem}
\begin{proof}
Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.  These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.

Begin by focusing on the $d^{th}$ component of $R_{D'}$: $(R_{D'})_d=H^0(X,\lfloor D+\frac{\alpha}{\beta}P\rfloor)$.  By our hypothesis (equation \ref{lem:deg_1_saturation_induction_dimension_condition}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{\alpha}{\beta}\rfloor>0$,
\[
	h^0(X,d(D+\frac{\alpha}{\beta}))=h^0(X,dD)+\deg(d\frac{\alpha}{\beta})
\]
so in $H^0(X,\lfloor dD'\rfloor)$ we can find elements with pole order $i$ at $P$ for any $i\in 0,...,\lfloor d\frac{\alpha}{\beta}\rfloor$.  We can use a method similar to O'Dorney to construct the $y_i$s as desired:

Let $0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}$ be the nonnegative best lower approximation of $\frac{\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of orders ranging from 0 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor=c_i$ at $P$.  For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction, so any product of $\prod z_i$ of elements of degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i}$, so we have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.  Thus, the elements of $R_{d_i}

 in fact a generic element in the respective degree will suffice.\todo{add proof of this; is the generic statement correct?}  Following O'Dorney's argument correctly gives that these along with $u$ (in degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{\alpha}{\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{D'})_d$ with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace consisting of elements only with nonzero pole at $P$.  Therefore, by pole considerations $y_1,...,y_n$ generate $(R_{D'})_d$ over $(R_{D})_d$, \todo{the word generate here is a little imprecise} so $u,x_1,...,x_m,y_1,...,y_n$ generate $R_{D'}$.
